%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Golang System Developer in Linux EDR team} % Job title
    {Graph inc - \textnormal{a cybersecurity company that offers an Advance Threat Detection system}} % Organization
    {Tehran, Iran} % Location
    {(2 yrs and 9 mos) Feb. 2021 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Develop client side of EDR (Endpoint Detection and Response) with \textbf{Golang} for Linux operating systems and ensured deployment on over 2000 Linux systems, resulting in awarded client security and enhanced threat detection capabilities.
        \begin{itemize}
            \item Established \textbf{gRPC} as the primary communication protocol between client and server, resulting in a 40\% reduction in latency and an overall improvement in system performance.
            \item Implement a log collector which gathers system logs (like \textbf{Audit} logs, \textbf{Fanotify} notifications) and sends to server. 
            \item Design an auto response mechanism that protects client against detected malware.
            \item Developed and implemented a dual service solution for both \textbf{Systemd} and \textbf{SysVinit}.
            \item Wrap product with \textbf{RPM} and \textbf{DEB} package which is compatible with CentOS, Red-hat, Ubuntu and Fedora distributions that covers 80\% of market’s customer systems.
            \item Launch an updater service with Golang that updates automatically the package.
            \item Enhanced the file processor module through the optimization of the Shannon algorithm, resulting in a notable 30\% decrease in CPU utilization and accelerated accuracy in file entropy calculations for effective identification of obfuscated files.
        \end{itemize}
        \item Restructured server side database using Golang's \textbf{Ent framework}, resulting in a 10\% decrease in query execution benchmark time.
        \item Customized comprehensive unit tests for Golang packages, ensuring code quality and reducing bug count by 40\%.
        \item Collaborated with stakeholders and business teams to understand customer requirements, resulting in redesign of features that increased customer satisfaction by 25\%.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Golang Developer} % Job title
    {Sanjagh - \textnormal{an advertising network platform that connects advertisers with publishers}} % Organization
    {Tehran, Iran} % Location
    {(5 mos) Feb. 2020 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Launched a highly efficient \href{https://github.com/pooria1/url-shortener}{URL Shortener} project during internship at Sanjagh, reducing link generation time by 50\% and improving overall website performance by optimizing URL redirects.
        \item Learned Producing APIs and writing \textbf{RESTful API} using \textbf{echo framework}.
        \item Created a cache service using Golang which caches response of another service. This cache improved response time up to 10 times faster.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
